\section{Introduction}

\paragraph{}
The need of immersion and realism in video games is increasing.
Developing a game makes the use of an already existing engine mandatory.
The C4Engine is one of them.
Amongst other features, it presents a solution for real time visualisation of volumetric data.
This algorithm, developed by Lengyel \cite{lengyel2010voxel}, will be reffered as Transvoxel in the rest of the paper.

\paragraph{}
Transvoxel renders volumetric data through rasterization.
It is based on Marching Cubes (MC) \cite{lorensen1987marching} to convert the dataset into a triangulated surface.
However, where MC is not adaptive, Lengyel's method adapts the resolution of the triangulation depending on the distance to the camera.
This adaptivity is handled by applying a modified MC on an octree structure.

\paragraph{}
Therefor Lengyel's method is based on modified MC and an octree.
MC is data parallel and thus can be implemented efficiently on a GPU.
However, the octree is an recursive structure and is then handled on the CPU.
Transvoxels is finally a rendering method that runs partly on the CPU and partly on the GPU.

\paragraph{}
It would be interesting to make this solution GPU only.
This would lead to a great speed up as GPUs are very efficient when running data parallel algorithms.
Furthermore, the implementation would be simplified, as the GPU and CPU would run asynchroneously.
Finally, this would leave the CPU free for other computational tasks.

\paragraph{}
To make this algorithm GPU only, the octree need to be linearised.
This non recursive representation have been developped by Gargantini \cite{gargantini1982effective} and efficiently GPU implemented by Dupuy \cite{dupuy2014quadtrees}.
By combining those linear octrees with Transvoxels, we obtain a method to render volumetric data entirely on the GPU.

\paragraph{}
Rasterizing this surface can only be done if all triangles projects onto more than a pixel.
Otherwise, aliasing artefacts appear.
Therefor we add a LoD criteria based on the triangles projected size.
This leads to a method that is 
\begin{itemize}
	\item Real time
	\item Keeping the triangles always bigger than a pixel
	\item GPU only to free the CPU
\end{itemize}